Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-04-06 prevalence_testing/postshocktest2022draft.tex
updated unemployment

\textcolor{red}{A lot is needed here. We need to say that we are assuming that government lockdowns are temporary or rather that the effect of government lockdowns will be temporary. We need to mention that none of the time series in the donor pool involve lockdowns. We should consider a few time horizons. Something like 2, 3, or 4 months ahead might be interesting (we may need to consider a less complex dynamic model for fitting purposes). I would guess that a shorter window may exhibit disagreement between the donor pool and the series under study or may show different decisions being reported. }

>>>>

Arguably the most watched macroeconomic indicator for the US economy is the monthly release of the total nonfarm payrolls, which reflects the gains or losses of persons employed.  However, its reputation as a lagging indicator of macroeconomic health constrains its usefulness.  This makes it ripe for forecasting under the method herein.  To this end, we examine the March 2020 lockdown measures as a shock to the US economy and labor market, enlisting previous macroeconomic shocks to the US economy as donors.  The donor pool assembled notably contains no cases of lockdowns or even pandemics or epidemics.  Instead, the common thread running through the time series under study and the donors is the element of a sudden and considerable surprise visited upon the economy from source previously judged to be marginal.

\textcolor{red}{A lot is needed here. We need to say that we are assuming that government lockdowns are temporary or rather that the effect of government lockdowns will be temporary. We need to mention that none of the time series in the donor pool involve lockdowns. We should consider a few time horizons. Something like 2, 3, or 4 months ahead might be interesting (we may need to consider a less complex dynamic model for fitting purposes). I would guess that a shorter window may exhibit disagreement between the donor pool and the series under study or may show different decisions being reported. However, don't we want to match the time series under study with donors based on only pre-shock features, data, variables, etc?  It might be good to think of donor selection as a two-stage matching procedure: first, a donor is judged worthy based on some qualitative or quantitative analysis (the latter of which can be simply the correlation of their covariate vectors at $T^{*}$); second, the matches are aggregated using distanced-based weighting.}
